\SW Extended! Snappy Titles!

### 2015-02-09 doc/sw-extended.tex
updates to agent and subject and sw-extended.tex

@@

\subsubsection{E-Step}
\label{sec:formalism:em:estep}
The E-Step is just taking the expected complete log-likelihood, or the
expectation value over $P(\cdot \ | x, \phi)$. This is equivalent to replacing
$z_j$ with $p_j$:
\begin{align}
  p_j &= \frac{1}{N_j} \sum_{i \in \Omega_j} P(z_j = 1 \ | \ x_{ij} ; \Phi) =
  \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ P(x_{ij} \ | \ z_j = 1; \Phi)
P(z_j = 1 ; \Phi)}{P(x_{ij} ; \Phi)} \\
&= \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ PL_{i}^{x_{ij}} (1 - PL_{i})^{(1 -
x_{ij})} p_{ij}^{0}}{ PL_{i}^{x_{ij}} (1 -
  PL_{i})^{(1 - x_{ij})} p_{ij}^{0} + PD_{i}^{(1 - x_{ij})} (1 -
PD_{i})^{x_{ij}} (1 - p_{ij}^{0})}
\end{align}
where $i \in \Omega_j$ is now the set of classifications done on the $j$-th
image and $N_j$ is the number of classifications done on the $j$-th image. This
makes sense: $p_{ij}^{0}$ is just the prior likelihood of an image being a lens,
while $PL_{i}$ is how well we would have identified a lens as such.

@@

>>>>

% TODO:
% Kamal Nigam, Andrew McCallum and Tom Mitchell. Semi-supervised Text Classification Using EM. In Chapelle, O., Zien, A., and Scholkopf, B. (Eds.) Semi-Supervised Learning. MIT Press: Boston. 2006.
% according to
% http://www.mblondel.org/journal/2010/06/21/semi-supervised-naive-bayes-in-python/#more-126
% this paper would be an example of the sort of thinking I had with the EM
% algorithm (not quite what was implimented in stage 2 at phil's request),
% where the E step just does the unlabeled, and the M step uses both labeled
% and unlabeled data

@@

\subsubsection{E-Step}
\label{sec:formalism:em:estep}
% TODO: reword. The maximization here is over the zj's, so word to make that clear.
% The E-Step is just taking the expected complete log-likelihood, or the
% expectation value over $P(\cdot \ | x, \phi)$.
The E-Step is maximizing the complete log-likelihood with respect to the image
probability $p_j$.  This is equivalent to replacing $z_j$ with $p_j$:
% TODO: replace this with equivalent like eq1
\begin{align}
  p_j &= \frac{1}{N_j} \sum_{i \in \Omega_j} P(z_j = 1 \ | \ x_{ij} ; \Phi) =
  \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ P(x_{ij} \ | \ z_j = 1; \Phi)
P(z_j = 1 ; \Phi)}{P(x_{ij} ; \Phi)} \\
&= \frac{1}{N_j} \sum_{i \in \Omega_j} \frac{ PL_{i}^{x_{ij}} (1 - PL_{i})^{(1 -
x_{ij})} p_{ij}^{0}}{ PL_{i}^{x_{ij}} (1 -
  PL_{i})^{(1 - x_{ij})} p_{ij}^{0} + PD_{i}^{(1 - x_{ij})} (1 -
PD_{i})^{x_{ij}} (1 - p_{ij}^{0})}
\end{align}
where $i \in \Omega_j$ is now the set of classifications done on the $j$-th
image and $N_j$ is the number of classifications done on the $j$-th image. This
makes sense: $p_{ij}^{0}$ is just the prior likelihood of an image being a lens,
while $PL_{i}$ is how well we would have identified a lens as such.

@@

\section{Validation of Training}
\label{sec:validation}

A validation dataset is needed to prevent overfitting training data and to try
to test how the training data does against real lenses. These need to come in
two categories: actual lens environments, and simulated lenses. The need for
two sets arises because of the paucity of actual lenses. In \SW, most training
objects are explicitly given to a user -- if a user incorrectly identifies a
training object, they are informed of that failure, and likewise for a correct
classification.

Problems:
0. By telling users about failures in the sim/dud, we explicitly break the
notion that users come in fully-formed. But we also need to give users
incentives to keep working, by rewarding them for good behavior. Replace by
current crowd assessments and telling them how they did compared with the
crowd?
1. \SW does not have any 'silent' training images which could function as
validation datasets, since you have broken the training by telling users.
2. How to manage the difference between 'dud known lens fields' and 'dud sim
fields'? Just put them together?
3. If you tell users about the correct sim classification, do you also tell
them about a correct lens classification, and do you tell them it was a real
lens?
4. Can I just use the dud fields?
